---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rflirtool

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![CRAN status](https://www.r-pkg.org/badges/version/rflirtool)](https://CRAN.R-project.org/package=rflirtool)
<!-- badges: end -->

# rflirtool: FLIR Data Processing Toolkit for vegetation plots at RMBL

## Overview

The **rflirtool** package is a comprehensive toolkit for processing and analyzing thermal data from FLIR camera at RMBL gradient, with a particular focus on vegetation research and analysis. It simplifies the handling of CSV data files generated by FLIR Tools software, making it easier to extract valuable insights from thermal images.

## Features

- Load and process thermal data from CSV files generated with FLIR Tools.
- Calculate the basic statistic data for temperature data.
- Perform statistical analysis on thermal datasets.
- Simplify the workflow for vegetation analysis with FLIR cameras.

## Installation

To install the latest development version from GitHub, you can use the `pak` package:

``` r
pak::pak("PaulESantos/rflirtool")
```


## Getting Started

Here's a quick example of how to use `rflirtools` to load and analyze thermal data:

- `get_flir_data_matrix()` 

```{r}
library(rflirtool)
filename <- system.file("extdata/1.csv", package = "rflirtool")

get_flir_data_matrix(filename) |> 
  tibble::as_tibble()
```

```{r}
filename1 <- system.file("extdata/mo_1-4_T_u.csv", package = "rflirtool")
get_flir_data_matrix(filename1) |> 
  tibble::as_tibble()
```


```{r}
filename1 <- system.file("extdata/rflirtool_1.csv", package = "rflirtool")
get_flir_data_matrix(filename1) |> 
  tibble::as_tibble()
```

- `get_flir_summary()`

```{r}
filename1 <- system.file("extdata/rflirtool_1.csv", package = "rflirtool")
get_flir_data_matrix(filename1) |> 
  get_flir_summary() |> 
  tibble::as_tibble()
```


```{r}
filename1 <- system.file("extdata/mo_1-4_T_u.csv", package = "rflirtool")
get_flir_data_matrix(filename1) |> 
  get_flir_summary() |> 
  tibble::as_tibble()
```
